Generating Images From Captions\\ With Attention

### 2015-10-30 iclr-paper-new.tex
changes

As for the quantitative comparison of different models, we first compare the performances of the model trained with variational methods. We rank the images in the test set conditioned on the captions based on the variational lower bound of likelihood and then report the Precision-Recall metric as an evaluation of the quality of the generative model (see Table~\ref{tab:results}.). Unsurprisingly, generative models didn't perform well in the image retrieval task. To deal with the large computational complexity involved in looping through each test image, we create a shortlist of one hundred images including the correct one, based on the images having the closest distance in the convolutional feature-space of a VGG-like model \citep{simonyan_convnet} trained on the CIFAR dataset\footnote{The architecture of the model is described here \url{http://torch.ch/blog/2015/07/30/cifar.html}. The shortlist of test images used for evaluation can be downloaded here \url{http://www.cs.toronto.edu/~emansim/cap2im/test-nns.pkl}.} \citep{krizhevsky_cifar}. 
Since there are ``easy'' images for which the model assigns high likelihood independent of the query caption, we look at the ratio of the likelihood of the image conditioned on the sentence to the likelihood of the image conditioned on the mean sentence representation in the training set \citep{kiros_captions}. 
We found that the reconstruction error $\rloss$ increased for sharpened images, and that sharpening considerably hurt the retrieval results. Since sharpening changes the statistics of images, computing reconstruction error for each pixel is not necessarily a good metric.

@@

%\newpage
\section{Acknowledgements}
We would like to thank developers of Theano \citep{theano} for a powerful software and authors of \citep{denton_lapgan} for open sourcing their code. We would also like to thank Ryan Kiros and Nitish Srivastava for helpful discussions. We will be releasing our code with pretrained models as soon as we clean it.

>>>>

As for the quantitative comparison of different models, we first compare the performances of the model trained with variational methods. We rank the images in the test set conditioned on the captions based on the variational lower bound of likelihood and then report the Precision-Recall metric as an evaluation of the quality of the generative model (see Table~\ref{tab:results}.). Unsurprisingly, generative models didn't perform well in the image retrieval task. To deal with the large computational complexity involved in looping through each test image, we create a shortlist of one hundred images including the correct one, based on the images having the closest distance in the convolutional feature-space of a VGG-like model \citep{simonyan_convnet} trained on the CIFAR dataset\footnote{The architecture of the model is described here \url{http://torch.ch/blog/2015/07/30/cifar.html}. The shortlist of test images used for evaluation can be downloaded here \url{http://www.cs.toronto.edu/~emansim/cap2im/test-nns.pkl}.} \citep{krizhevsky_cifar}. 
Since there are ``easy'' images for which the model assigns high likelihood independent of the query caption, we look at the ratio of the likelihood of the image conditioned on the sentence to the likelihood of the image conditioned on the mean sentence representation in the training set \citep{kiros_captions}.
We found that the lower bound of log likelihood decreased for sharpened images, and that sharpening considerably hurt the retrieval results. Since sharpening changes the statistics of images, computing reconstruction error for each pixel is not necessarily a good metric.

@@

%\newpage
\section{Acknowledgements}
We would like to thank developers of Theano \citep{theano} for a powerful software and authors of \citep{denton_lapgan} for open sourcing their code. We would also like to thank Ryan Kiros and Nitish Srivastava for helpful discussions. We will be releasing our code with pretrained models

### 2015-10-30 supp.tex
changes

Each parameter in alignDRAW was initialized by sampling from the Gaussian distribution of mean $0$ and standard deviation of $0.01$. The model was trained using \textit{RMSProp} with initial learning rate of $0.001$. The norm of the gradients was clipped to $10.0$ during training to deal with exploding gradients. For all tasks we used $128$ units in the language model and $512$ units in the $tanh$ perceptron in the alignment function. For the Microsoft COCO task, the alignDRAW model was trained for $18$ epochs and the learning rate was reduced by the factor of $0.1$ after $11$ epochs. The architectural configurations of alignDRAW models are shown on Table~\ref{tab:drawhyper}.

@@

The LAPGAN model used for sharpening had the same configuration as the $28 \times 28$ model trained by \cite{denton_lapgan} on the edge residuals of CIFAR dataset.  that can be found at \url{https://gist.github.com/soumith/e3f722173ea16c1ea0d9}. The model was trained for $6$ epochs.

>>>>

Each parameter in alignDRAW was initialized by sampling from the Gaussian distribution of mean $0$ and standard deviation of $0.01$. The model was trained using \textit{RMSprop} with initial learning rate of $0.001$. The norm of the gradients was clipped to $10.0$ during training to deal with exploding gradients. For all tasks, $\overrightarrow{h}^{lang}_{n}$ and $\overleftarrow{h}^{lang}_{n}$ in the language model had $128$ units, and vector $v$ in \textit{align} perceptron had $512$ units. For the Microsoft COCO task, the alignDRAW model was trained for $18$ epochs and the learning rate was reduced by the factor of $0.1$ after $11$ epochs. The architectural configurations of alignDRAW models are shown on Table~\ref{tab:drawhyper}.

@@

The GAN model used for sharpening had the same configuration as the $28 \times 28$ model trained by \cite{denton_lapgan} on the edge residuals of CIFAR dataset. The configuration can be found at \url{https://gist.github.com/soumith/e3f722173ea16c1ea0d9}. The model was trained for $6$ epochs.
